---
title: "Basic Inferential Data Analysis Instructions"
author: "Dongjun_Cho"
date: "7/3/2020"
output:
  pdf_document: default
  html_document: default
---

##  Load the ToothGrowth data and perform some basic exploratory data analyses
```{r}
data(ToothGrowth)
data <- ToothGrowth
head(data)
dim(data)

```

##  Provide a basic summary of the data.
```{r}
summary(data)
library(ggplot2)
ggplot(data, aes(x= supp, y = len, fill=supp)) + geom_bar(stat="identity")+labs(x= "Dose", y="Tooth") +  facet_grid(. ~ dose)

```

##  Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)

Hypothesis Tests for length 0.5
```{r}
OJ_supp_05  = ToothGrowth$len[ToothGrowth$supp== 'OJ' & ToothGrowth$dose==0.5]
VC_supp_05  = ToothGrowth$len[ToothGrowth$supp== 'VC' & ToothGrowth$dose==0.5]

t.test(OJ_supp_05, VC_supp_05, alternative = "greater", paired = FALSE)

```

Hypothesis Tests for length 1.0
```{r}
OJ_supp_10  = ToothGrowth$len[ToothGrowth$supp== 'OJ' & ToothGrowth$dose==1.0]
VC_supp_10  = ToothGrowth$len[ToothGrowth$supp== 'VC' & ToothGrowth$dose==1.0]

t.test(OJ_supp_10, VC_supp_10, alternative = "greater", paired = FALSE)

```


Hypothesis Tests for length 2.0
```{r}
OJ_supp_20  = ToothGrowth$len[ToothGrowth$supp== 'OJ' & ToothGrowth$dose==2.0]
VC_supp_20  = ToothGrowth$len[ToothGrowth$supp== 'VC' & ToothGrowth$dose==2.0]

t.test(OJ_supp_20, VC_supp_20, alternative = "greater", paired = FALSE)

```

##  State your conclusions and the assumptions needed for your conclusions.
In general, OJ provides higher tooth growth then VC.
Increase rate of dose and tooth growth are proportional.